---
title: "gtsummary in quarto"
format: 
  html:
    theme: journal
execute: 
  cache: false
---

```{r}
#| echo: false
glasses_f <- 32
glasses_m <- 38
glasses_comparison <- if (glasses_f > glasses_m) "greater" else "lower"
```
A `r glasses_comparison` proportion of female (`r glasses_f`) than male (`r glasses_m`) participants wore glasses.



```{r}
#| output: false
# output:false to remove all output (including the messages), message: false to remove messages, include: false to remove all output and code, 
library(tidyverse)
library(gtsummary)
nlsy_cols <- c("glasses", "eyesight", "sleep_wkdy", "sleep_wknd", 
               "id", "nsibs", "samp", "race_eth", "sex", "region", 
               "income", "res_1980", "res_2002", "age_bir")
nlsy <- read_csv(here::here("data", "raw", "nlsy.csv"), 
                 na = c("-1", "-2", "-3", "-4", "-5", "-998"),
                 skip = 1, col_names = nlsy_cols) |> 
  mutate(region_cat = factor(region, labels = c("Northeast", "North Central", "South", "West")),
         sex_cat = factor(sex, labels = c("Male", "Female")),
         race_eth_cat = factor(race_eth, labels = c("Hispanic", "Black", "Non-Black, Non-Hispanic")),
         eyesight_cat = factor(eyesight, labels = c("Excellent", "Very good", "Good", "Fair", "Poor")),
         glasses_cat = factor(glasses, labels = c("No", "Yes"))) 
```

```{r}
sleep_avg <- mean(nlsy$sleep_wkdy, na.rm = TRUE)
```

The average hours of sleep was `r round(sleep_avg, 1)`

I also really like to use the `scales::number()` function for formatting numbers: `scales::number(sleep_avg, accuracy = 0.1)` = `r scales::number(sleep_avg, accuracy = 0.1)`

# Customization of `tbl_summary()`

```{r}
#| label: tbl-descriptive
#| tbl-cap: "Descriptive statistics about the sample"
table1 <- tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir))
# have to print "table1" for it to be shown, and for the caption to show up
table1
```

As you can see in @tbl-descriptive, more female (`r inline_text(table1, variable = "glasses", column = "Female")`) than male (`r inline_text(table1, variable = "glasses", column = "Male")`) wear glasses. This is also shown in @tbl-nicer, in which the glasses label is capitalized.


```{r}
#| label: tbl-nicer
#| tbl-cap: "More nicely labeled descriptive statistics about the sample"
tbl_summary(
  nlsy,
  by = sex_cat,
  include = c(sex_cat, race_eth_cat, region_cat,
              eyesight_cat, glasses, age_bir),
  label = list(
    race_eth_cat ~ "Race/ethnicity",
    region_cat ~ "Region",
    eyesight_cat ~ "Eyesight",
    glasses ~ "Wears glasses",
    age_bir ~ "Age at first birth"
  ),
  missing_text = "Missing")
```
